Letter to Reviewers of Submission \#341

### 2015-06-27 introduction.tex
it's only the right column of the 8th page.

Fortunately, there is abundant evidence that technology can
solve many of these problems.
Gutierrez's interviews with data scientists~\cite{Gutierrez:2014:DSA}, 
include the following:

>>>>

Fortunately, there is evidence that appropriate technology might
solve some of these problems.  Gutierrez's interviews with data
scientists~\cite{Gutierrez:2014:DSA} include the following quotes:
